---
title: "GHG Electricity"
author: "JV"
format: html
code-fold: true
---
# Introduction

# Data (EEA)

Data taken from European Environement Agency

[EEA](https://www.eea.europa.eu/en)



## Download Data

```{r}
#| warning: false
#| message: false


# Data from EEA Homepage

library(tidyverse)

#gCO2e/kWh

df<-read.csv("https://www.eea.europa.eu/data-and-maps/daviz/co2-emission-intensity-14/download.csv") # %>%
  # filter(Member.State.text=="EU-27")

head(df)

```

## Boxplots GHG Intensity of Electricity in  Member States

```{r}
#| warning: false
#| message: false

library(ggrepel)

df %>% filter(Member.State.text!="EU-27",
              Year.year %in% c(1990, 2000, 2010, 2020)) %>% #View() %>% 
  ggplot(aes(Year.year, Greenhouse.gas..GHG..emission.intensity.number.1, group=Year.year, label=Member.State.text))+
  geom_boxplot()+
  geom_point(alpha=.5)+
  geom_text_repel()+ # tbd: Select Member States
  theme_light()+
  labs(title="GHG-Intensity in Electricity Generation",
       x="Year",
       y="GHG-Intensity gCO2e/kWh",
       caption = paste("Illustration: cep, Data: European Environment Agency, Data Download:", Sys.Date(),  sep = " "))
```


## History and Trend GHG Intensity of Electricity in EU

```{r}
#| message: false
#| warning: false

cep1 <- I(rgb(133/255, 43/255, 65/255, 1))

df %>%
  filter(Member.State.text=="EU-27") %>%
  arrange(Year.year) %>%
#   fill(Greenhouse.gas..GHG..emission.intensity.number.1,.direction = "down") %>%
ggplot(aes(Year.year, Greenhouse.gas..GHG..emission.intensity.number.1, ))+
  geom_point(color=cep1)+
  #geom_line()+
 # geom_point(aes(y=Indicative.level.high.number), color="red")+
#  geom_point(aes(y=Indicative.level.low.number), color="red")+
  geom_smooth(method='glm', fullrange=T, se=F)+ # linear
  #geom_smooth(method='glm', formula = y~x + I(x^2),
     # method.args = list(family = gaussian(link = 'log')),
#  fullrange =T, color = "orange")+
 geom_smooth(method="glm",
             formula = y ~ x + I(x^2), fullrange =T,color="green", se=F)+ # quadratic
  xlim(min(df$Year.year), 2050)+
  ylim(0, max(df$Greenhouse.gas..GHG..emission.intensity.number.1))+
  theme_light()+
  labs(title="GHG-Intensity in Electricity Generation - EU",
       x="Year",
       y="GHG-Intensity gCO2e/kWh",
       caption = paste("Blue line: linear trend, green line: quadratic trend; Illustration: cep, Data: European Environment Agency, Data Download:", Sys.Date(),  sep = " "))
```


## History and Trend GHG Intensity of Electricity in selected Member States


```{r}
#| message: false
#| warning: false

df %>%
  filter(Member.State.text %in% c("France", "Germany", "Poland")) %>%
 # arrange(Year.year) %>%
#   fill(Greenhouse.gas..GHG..emission.intensity.number.1,.direction = "down") %>%
ggplot(aes(Year.year, Greenhouse.gas..GHG..emission.intensity.number.1, ))+
  geom_point()+
  #geom_line()+
 # geom_point(aes(y=Indicative.level.high.number), color="red")+
 # geom_point(aes(y=Indicative.level.low.number), color="red")+
  geom_smooth(method='glm', fullrange=T, se=F)+ # linear
  #geom_smooth(method='glm', formula = y~x + I(x^2),
     # method.args = list(family = gaussian(link = 'log')),
#  fullrange =T, color = "orange")+
 #geom_smooth(method="glm",
       #      formula = y ~ x + I(x^2), fullrange =T,color="green")+ # quadratic
  xlim(min(df$Year.year), 2050)+
  ylim(0, max(df$Greenhouse.gas..GHG..emission.intensity.number.1))+
  theme_light()+
  facet_wrap(~Member.State.text,
# scales="free_y"
)+
  labs(title="GHG-Intensity in Electricity Generation - Selected Member States",
       x="Year",
       y="GHG-Intensity gCO2e/kWh",
       caption = paste("Blue line: linear trend; llustration: cep, Data: European Environment Agency, Data Download:", Sys.Date(),  sep = " "))
```


[Die drei Länder in einem Chart]::


```{r}
#| message: false
#| warning: false

cep1 <- I(rgb(133/255, 43/255, 65/255, 1))
cep2 <- I(rgb(133/255, 43/255, 65/255, .75))
cep3 <- I(rgb(133/255, 43/255, 65/255, .5))


df %>%
  filter(Member.State.text %in% c("France", "Germany", "Poland")) %>%
 # arrange(Year.year) %>%
#   fill(Greenhouse.gas..GHG..emission.intensity.number.1,.direction = "down") %>%
ggplot(aes(Year.year, Greenhouse.gas..GHG..emission.intensity.number.1, group= Member.State.text, color=Member.State.text ))+
  geom_point()+
  #geom_line()+
 # geom_point(aes(y=Indicative.level.high.number), color="red")+
 # geom_point(aes(y=Indicative.level.low.number), color="red")+
  geom_smooth(method='glm', fullrange=T, se=F, color="blue")+ # linear
  #geom_smooth(method='glm', formula = y~x + I(x^2),
     # method.args = list(family = gaussian(link = 'log')),
#  fullrange =T, color = "orange")+
 #geom_smooth(method="glm",
       #      formula = y ~ x + I(x^2), fullrange =T,color="green")+ # quadratic
  xlim(min(df$Year.year), 2050)+
  ylim(0, max(df$Greenhouse.gas..GHG..emission.intensity.number.1))+
  scale_color_manual(values=c(cep3, cep2, cep1))+
  theme_light()+
#  facet_wrap(~Member.State.text,
# scales="free_y"
#)+
  labs(title="GHG-Intensity in Electricity Generation - Selected Member States",
       x="Year",
       y="GHG-Intensity gCO2e/kWh",
       color="Member States",
       caption = paste("Blue line: linear trend; llustration: cep, Data: European Environment Agency, Data Download:", Sys.Date(),  sep = " "))
```


## History and Trend GHG Intensity of Electricity in all Member States
```{r, fig.height=20}
#| message: false
#| warning: false

df %>%
  filter(Member.State.text !="EU-27") %>%
  arrange(Year.year) %>%
#   fill(Greenhouse.gas..GHG..emission.intensity.number.1,.direction = "down") %>%
ggplot(aes(Year.year, Greenhouse.gas..GHG..emission.intensity.number.1, ))+
  geom_point()+
  #geom_line()+
#  geom_point(aes(y=Indicative.level.high.number), color="red")+
  #geom_point(aes(y=Indicative.level.low.number), color="red")+
  geom_smooth(method='glm', fullrange=T)+ # linear
  #geom_smooth(method='glm', formula = y~x + I(x^2),
     # method.args = list(family = gaussian(link = 'log')),
#  fullrange =T, color = "orange")+
# geom_smooth(method="glm",
#             formula = y ~ x + I(x^2), fullrange =T,color="green")+ # quadratic
  xlim(min(df$Year.year), 2050)+
  ylim(0, max(df$Greenhouse.gas..GHG..emission.intensity.number.1))+
  theme_light()+
  facet_wrap(~Member.State.text, scales="free_y", ncol = 3)+
  labs(title="GHG-Intensity in Electricity Generation - Member States",
       x="Year",
       y="GHG-Intensity gCO2e/kWh",
       caption = paste("llustration: cep, Data: European Environment Agency, Data Download:", Sys.Date(),  sep = " "))
```


# Technology Diffusion

```{r}
# Bibliotheken laden
library(ggplot2)

# Wertebereich für x festlegen
#x <- seq(-5, 5, 0.1)

sigmoid <- function(x) {
  1/ (1 + exp(-x))
}

#Farbe

cep <- I(rgb(133/255, 43/255, 65/255))

# Plot mit ggplot2 erstellen
ggplot() +
  stat_function(fun = sigmoid,
                color=cep,
                linewidth=1.5) +
  # geom_segment(aes(x=0, xend=0, y=0, yend=1), linetype=1) +
  #  annotate("segment", x = 0, xend = 0, y = 0, yend = 1,
  # linetype = "dashed")+
  annotate("rect", xmin = -5.5, xmax = -3.5, ymin = 0, ymax = 1,
           fill=cep, alpha = .05)+
  annotate("rect", xmin = -1.5, xmax = 1.5, ymin = 0, ymax = 1,
           fill=cep, alpha = .05)+
  annotate ("text", x= -7, y=.3, size= 14/.pt, label="I")+
  annotate ("text", x= -4.5, y=.3, size= 14/.pt, label="II")+
  annotate ("text", x= -2.5, y=.3, size= 14/.pt, label="III")+
  annotate ("text", x= 0, y=.3, size= 14/.pt, label="IV")+
  annotate ("text", x= 3.5, y=.3, size= 12/.pt, label="V")+
  scale_x_continuous(limits=c(-8,5),
                     breaks= NULL,
                     expand = c(0, 0))+
  scale_y_continuous(breaks =NULL,
                     expand = c(0, 0))+
  labs(      title = "Stylized Curve of Technology Diffusion",
             x = "Time",
             y = "Level of Adoption",
             caption ="I: Solution Search, II: Proof of Concept, III: Early Adopters, IV: System Integration, V: Market Expansion.\n Illustration: cep based on Speelman, L. / Novata Y. (2022).") +
  theme_classic(base_size= 12)
```

# EV Fleet in EU: New Cars

```{r}
#| message: false
#| warning: false
#| 
library(eurostat)

df1 <- get_eurostat("road_eqr_carpda",
                  type = "label",
                   time_format = "num",
                       select_time="Y",
                       cache = T
                 ) %>%
             filter(mot_nrg=="Electricity") %>%
             rename(electric=values) %>%
             select(geo, TIME_PERIOD, electric)

#head(df1)

#unique(df1$geo)

#Es gibt keine Angaben für EU

# EU-Staaten filtern

#Befehl definieren
`%notin%` <- Negate(`%in%`)

df1 <- df1 %>% filter(geo %notin% c("Albania", "United Kingdom",
                      "Türkiye", "Kosovo*", "Montenegro", "Bosnia and Herzegovina",
                       "Serbia", "Switzerland", "North Macedonia", "Norway", "Iceland",
                        "Georgia", "Moldova", "Liechtenstein"))
#length(unique(df1$geo))
#unique(df1$geo)
#Slowakei nicht im sample?

# EU aggregieren

df_EU <- df1 %>% group_by(TIME_PERIOD) %>%
                 summarise(electric=sum(electric))%>%
                 mutate(geo = 'European Union - 27 countries (from 2020)')


#View(df_EU)

df1 <- rbind(df1, df_EU)

#unique(df1$geo)

#length(unique(df1$geo))


#head(df1)

#df1 %>% filter(geo== 'European Union - 27 countries (from 2020)',
     #          TIME_PERIOD == 2020) %>%
       # head()

#View(df1)

df2 <- get_eurostat("road_eqr_carmot",
                  type = "label",
                  time_format = "num",
                  select_time="Y",
                  cache = T
                 ) %>%
             filter(mot_nrg=="Total") %>%
             rename(total=values) %>%
             select(geo, TIME_PERIOD, total)


#head(df2)

#unique(df2$geo)

df <- left_join(df1, df2)

#head(df)

#df %>% filter(geo=='European Union - 27 countries (from 2020)',
             #  TIME_PERIOD== 2020) %>%
       #head()


df <- df %>% mutate(share_ev = electric/total)

#df %>% filter(TIME_PERIOD == 2020,
#               geo==   'European Union - 27 countries (from 2020)')%>% head()

#head(df)


#df %>% filter(geo=='European Union - 27 countries (from 2020)',
       #       TIME_PERIOD== 2020) %>%
   #   head()

# plot

df%>% filter(geo=='European Union - 27 countries (from 2020)') %>%
      ggplot(aes(TIME_PERIOD, share_ev))+
      geom_point()+
      geom_smooth()+
      theme_light()

```

# EV Fleet in EU: Stock

```{r}
#| message: false
#| warning: false

df1 <- get_eurostat("road_eqs_carpda",
                  type = "label",
                   time_format = "num",
                       select_time="Y",
                       cache = T
                 )

#head(df1)


#df1 %>% filter(geo == 'European Union - 27 countries (from 2020)') %>% View()

# Keine Anteile Electric für EU

# EU-Staaten filtern

#Befehl definieren
`%notin%` <- Negate(`%in%`)

df1a <- df1 %>% filter(geo %notin% c("Albania", "United Kingdom",
                      "Türkiye", "Kosovo*", "Montenegro", "Bosnia and Herzegovina",
                       "Serbia", "Switzerland", "North Macedonia", "Norway", "Iceland",
                        "Georgia", "Moldova", "Liechtenstein"))

# unique(df1a$geo)
df1b <- df1a %>% filter(mot_nrg == 'Electricity') %>%
              select(geo, TIME_PERIOD,  values) %>%
              rename(electric = values)




df_EU <- df1b %>% group_by(TIME_PERIOD) %>%
                 summarise(electric=sum(electric))%>%
                 mutate(geo = 'European Union - 27 countries (from 2020)')
df1c <- rbind(df1b, df_EU)

df2 <- df1 %>% filter(mot_nrg == 'Electricity') %>%
              select(geo, TIME_PERIOD,  values) %>%
              rename(electric = values)

#head(df2)


df3 <- df1 %>% filter(mot_nrg == 'Total') %>%
              select(geo, TIME_PERIOD,  values) %>%
              rename(total = values)

#head(df3)

df <- left_join(df1c, df3) %>%
      mutate(share= electric/total)

#head(df)

df %>% filter(geo=='European Union - 27 countries (from 2020)') %>%
       ggplot(aes(TIME_PERIOD, share))+
       geom_point()+
       geom_line()+
      # geom_smooth()+
       theme_light()

```



